---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  fig.path = "README-"
)
```

# prevederer

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/prevederer)](https://cran.r-project.org/package=prevederer)
[![Travis build status](https://travis-ci.org/wkdavis/prevederer.svg?branch=master)](https://travis-ci.org/wkdavis/prevederer)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/wkdavis/prevederer?branch=master&svg=true)](https://ci.appveyor.com/project/wkdavis/prevederer)
[![Codecov test coverage](https://codecov.io/gh/wkdavis/prevederer/branch/master/graph/badge.svg)](https://codecov.io/gh/wkdavis/prevederer?branch=master)
[![CRAN RStudio mirror downloads](http://cranlogs.r-pkg.org/badges/prevederer)](http://www.r-pkg.org/pkg/prevederer)
[![Project Status: Active – The project has reached a stable, usable state and is being actively developed.](https://www.repostatus.org/badges/latest/active.svg)](https://www.repostatus.org/#active)
[![Lifecycle - maturing](https://img.shields.io/badge/lifecycle-maturing-blue)](https://www.tidyverse.org/lifecycle/#maturing)
![CRAN/METACRAN](https://img.shields.io/cran/l/prevederer)
<!-- badges: end -->

## Overview

prevederer is an R package for accessing the Prevedere API. Access to the 
Prevedere API requires an API key.

## Installation

```{r install-cran, eval = FALSE}
install.packages("prevederer")
```

### Development version

```{r install-dev, eval = FALSE}
devtools::install_github("wkdavis/prevederer") 
```

## Usage

### Endpoints
- `indicator`: returns basic information about an indicator.
- `indicator_series`: returns the data for an indicator.
- `correlation`: calculates Pearson's r and other statistics at different offsets between an endogenous and exogenous indicator.
- `raw_model`: returns all information about a forecast model.
- `forecast`: returns historical fit and forecasted values of a forecast model.
- `workbench`: returns the indicators used in a workbench.

### Example
```{r example, eval = FALSE}
library(prevederer)

api_key = "xyz123"
provider = "provider_a"
provider_id = "a123"

prevedere_indicator_series(api_key, provider, provider_id)
```
